\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\subsubsection{Notation and organization}
We use boldfaced small letters for vectors, and boldfaced capital letters for matrices. The set of natural numbers, real numbers and complex numbers are denoted as $\mathbb{N}$, $\mathbb{R}$, and $\mathbb{C}$, respectively. The symbol $\nabla_{\bm{x}}$ denotes the Euclidean gradient operator with respect to (w.r.t.) the vector $\bm{x}$. Thus, $\nabla_{\bm{x}}\cdot$ stands for the divergence, and $\Delta_{\bm{x}}$ stands for the Laplacian w.r.t. vector $\bm{x}$. We use $\langle\cdot,\cdot\rangle$ to denote the standard Euclidean inner product. The real and imaginary parts of a complex number $z$ are denoted via $\Re(z)$ and $\Im(z)$, respectively. The uniform probability distribution over an interval $[a,b]$ is denoted as ${\rm{Unif}}\left([a,b]\right)$. Likewise, the $n$ dimensional uniform probability distribution over $[a,b]^{n}$ is denoted as ${\rm{Unif}}\left([a,b]^{n}\right)$. The symbol $\propto$ denotes proportionality, $|\cdot|$ denotes the absolute value, $\|\cdot\|_{2}$ denotes the standard Euclidean 2-norm, $\otimes$ denotes the Kronecker product, $\det(\cdot)$ stands for the determinant, and the subscript $_{\sharp}$ denotes the pushforward of a PDF via a map. The $n\times n$ identity and zero matrices are denoted as $\bm{I}_{n}$ and $\bm{0}_{n\times n}$, respectively.

@@

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}. For completeness, the overall proximal algorithm is {\red{given}}.

>>>>

\subsubsection{Notation and organization}
We use boldfaced small letters for vectors, and boldfaced capital letters for matrices. The set of natural numbers, real numbers and complex numbers are denoted as $\mathbb{N}$, $\mathbb{R}$, and $\mathbb{C}$, respectively. The symbol $\nabla_{\bm{x}}$ denotes the Euclidean gradient operator with respect to (w.r.t.) the vector $\bm{x}$. Thus, $\nabla_{\bm{x}}\cdot$ stands for the divergence, and $\Delta_{\bm{x}}$ stands for the Laplacian w.r.t. vector $\bm{x}$. We use $\langle\cdot,\cdot\rangle$ to denote the standard Euclidean inner product. The real and imaginary parts of a complex number $z$ are denoted via $\Re(z)$ and $\Im(z)$, respectively. The uniform probability distribution over an interval $[a,b]$ is denoted as ${\rm{Unif}}\left([a,b]\right)$. Likewise, the $n$ dimensional uniform probability distribution over $[a,b]^{n}$ is denoted as ${\rm{Unif}}\left([a,b]^{n}\right)$. The symbol $\propto$ denotes proportionality, $|\cdot|$ denotes the absolute value, $\|\cdot\|_{2}$ denotes the standard Euclidean 2-norm, $\otimes$ denotes the Kronecker product, $\odot$ and $\oslash$ respectively denote the elementwise (Hadamard) product and division, $\det(\cdot)$ stands for the determinant, and the subscript $_{\sharp}$ denotes the pushforward of a PDF via a map. The $n\times n$ identity and zero matrices are denoted as $\bm{I}_{n}$ and $\bm{0}_{n\times n}$, respectively.

@@

\begin{algorithm}[t]
\caption{Proposed proximal algorithm for $\bm{\varrho}_{k-1}\mapsto\bm{\varrho}_{k}$}
\label{KineticProxAlgorithm}
\begin{algorithmic}[1]
\Procedure{ProxRecursion}{$\bm{\varrho}_{k-1}, h, \varepsilon, N, \delta, L$}
\For{$i=1$ to $N$}
\State $\bm{\zeta}_{k-1}(i) \gets \exp\left(-\left(\bm{\eta}_{k-1}^{i}\right)^{\top}\bm{\eta}_{k-1}^{i}-1\right)$
\For{$j=1$ to $N$}
\State $\bm{C}_{k}(i,j) \gets \parallel\bm{\eta}_{k-1}^{j} - \bm{\eta}_{k}^{i}+ h\nabla U(\bm{\xi}_{k}^{i})\parallel_{2}^{2}$
\State \qquad\quad $+12\bigg\|\dfrac{\bm{\xi}_{k-1}^{j}-\bm{\xi}_{k}^{i}}{h} - \dfrac{\bm{\eta}_{k-1}^{j} + \bm{\eta}_{k}^{i}}{2}\bigg\|_{2}^{2}$
\EndFor
\EndFor
\State $\bm{\Gamma}_{k} \gets \exp\left(-\bm{C}_{k}/2\varepsilon\right)$ \Comment{elementwise exponential}
\State $\bm{z}_{0} \gets {\rm{rand}}_{N\times 1}$ \Comment{random vector of size $N\times 1$}
\State $\bm{z} \gets \left[\bm{z}_{0}, \bm{0}_{N\times(L-1)}\right]$ \Comment{initialize}
\State $\bm{y} \gets \left[\bm{\varrho}_{k-1}\oslash\left(\bm{\Gamma}_{k}\bm{z}_{0}\right), \bm{0}_{N\times(L-1)}\right]$ \Comment{initialize}
\State $\ell = 1$
\While{$\ell\leq L$}
\State $\bm{z}(:,\ell+1) \gets \left(\bm{\zeta}_{k-1}\oslash\left(\bm{\Gamma}_{k}^{\top}\bm{y}(:,\ell)\right)\right)^{\frac{1}{1+2\varepsilon/h}}$
\State $\bm{y}(:,\ell+1) \gets \bm{\varrho}_{k-1} \oslash \left(\bm{\Gamma}_{k}\bm{z}(:,\ell+1)\right)$
\If{$\|\bm{y}(:,\ell+1)-\bm{y}(:,\ell)\|_{2}<\delta$ \& $\|\bm{z}(:,\ell+1)-\bm{z}(:,\ell)\|_{2}<\delta$} \Comment{error within tolerance}
\State break
\Else
\State $\ell \gets \ell + 1$
\EndIf
\EndWhile\\
\Return $\varrho_{k} \gets \bm{z}(:,\ell) \odot \left(\bm{\Gamma}_{k}^{\top}\bm{y}(:,\ell)\right)$ \Comment{proximal update}
\EndProcedure	
\end{algorithmic}
\end{algorithm}

Finally, we transform the proximal updates back to the $\left(\bm{\theta},\bm{\omega}\right)^{\top}$ state space via the pushforward $\bm{\Psi}^{-1}$ as
\begin{align}
\varrho_{k}\left(\bm{\theta}_{k}^{i},\bm{\omega}_{k}^{i}\right) &= \bm{\Psi}^{-1}_{\sharp} \tilde{\varrho}_{k}\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right) \nonumber\\
&= \left(\prod_{j=1}^{n}m_{j}/\sigma_{j}\right)^{\!\!2}\tilde{\varrho}_{k}\left(\bm{M}\bm{\Sigma}^{-1}\bm{\theta}_{k}^{i},\bm{M}\bm{\Sigma}^{-1}\bm{\omega}_{k}^{i}\right),
\label{BringBackOriginalStateSpace}	
\end{align}
for all $i=1,\hdots,N$. The $\varrho_{k}\left(\bm{\theta},\bm{\omega}\right)$ from \eqref{BringBackOriginalStateSpace} approximates $\rho(t,\bm{\theta},\bm{\omega})$ (the transient solution of \eqref{KineticFPK}) in the sense \eqref{ConvergenceGuarantee}.

For completeness, the overall proximal algorithm is {\red{given}}. Its convergence guarantees can be found in \cite[Sec. III.C]{caluya2019TAC}.
